Neurology III

### 2017-09-08 neuro3.rmd
Fixed name of document...

---
title: "Module II"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document
documentclass: article
classoption: a4paper
urlcolor: blue
---

>>>>

---
title: "Neurology III"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document
documentclass: article
classoption: a4paper
urlcolor: blue
---
